target_offtarget

### 2025-03-29 manuscript_figures.Rmd
Changing virus load axis label to genome copies and background to M1 and M2

read_count <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab("log10(Viral Reads)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_count_norm1 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts1),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab("log10(viral reads/cleaned reads)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

read_count_norm2 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = (Viral.load),
    y = log10(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab("Log (viral reads/cleaned reads/genome length)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab("Log (mean read depth)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

total_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (total_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  # ggtitle("All") +
  ylab("Total number of reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

viral_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (viral_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  # ggtitle("Viral reads") +
  ylab("Number of viral reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

ATCC_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (ATCC_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  ggtitle("Spike-in Viral Reads") +
  ylab("Spike-in Viral Reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

prop_ATCC <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_ATCC, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  ggtitle("Spike-in viral reads") +
  ylab("Proportion") +
  scale_color_manual(values = cols2, labels = c("P1", "P2"))

prop_viral <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_viral, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
 scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  # ggtitle("Viral reads") +
  ylab("Proportion of viral reads") +
  scale_color_manual(values = cols2, labels = c("P1", "P2")) + scale_y_continuous(limits=c(0,1.0))

@@

facet_names_bg <- c(
  "dedup_TE" = "Deduplicated",
  "nodedup_TE" = "Non-Deduplicated",
  "p2" = "P1",
  "p8" = "P2"
)

@@

background_counts_reads <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels =
      c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
      )
  ) +
  scale_x_log10(labels = scales::label_log10()) +
  ylab("log10(Viral Reads)")

backgrounds_counts_reads_norm <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts1),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_bw() +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(label = scales::label_log10()) +
  ylab("log10(viral reads/cleaned reads)")

backgrounds_counts_reads_norm2 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(labels = scales::label_log10()) +
  ylab("log10(viral reads/cleaned reads/genome length)")

background_read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray"),
    axis.title.y = element_text(size = 10),
    legend.title = element_blank()
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(label = scales::label_log10()) +
  ylab("log10(mean read depth)")

@@

persite_coverage_both |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  ggplot(aes(x = virus, y = percent_coverage, colour = Background)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_dodge(width = .75)) +
  facet_grid(~as.character(Viral.load), labeller = label_parsed) +
  theme_few() +
  ylab("Genome coverage") +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(values = cols2, labels = c("P1", "P2")) +
  scale_x_discrete(
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_y_continuous(limits = c(0, 1))

@@

coverage_labels3 <-c("100" = "1e+02",
                    "1000" = "1e+03",
                    "100000" = "1e+05",
                    "p2" = "P1",
                    "p8"= "P2")

@@

persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Human_respiratory_syncytial_virus") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id, label = label_parsed) +
  ylab("Coverage") +
  ggtitle("Human RSV (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("P1", "P2"))
```

@@

persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Zika_virus") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id, label = label_parsed) +
  ylab("Coverage") +
  ggtitle("Zika virus (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("P1", "P2"))

@@

facet_names <- c(
  "Msp_p2" = "P1",
  "Msp_p8" = "P2",
  "off_target" = "Background",
  "on_target" = "Spike-in"
)

>>>>

read_count <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab(" Log (Viral Reads)") +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  ylab("Log (Viral Reads)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_count_norm1 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts1),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(3, 1)) +
  ylab("Log (viral reads/cleaned reads)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

read_count_norm2 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = (Viral.load),
    y = log10(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(3, 1)) +
  ylab("Log (viral reads/cleaned reads/genome length)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(3, 1)) +
  ylab("Log (mean read depth)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

total_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (total_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  # ggtitle("All") +
  ylab("Total number of reads") +
  scale_color_manual(values = cols2, labels = c("M1", "M2"))

viral_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (viral_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  # ggtitle("Viral reads") +
  ylab("Number of viral reads") +
  scale_color_manual(values = cols2, labels = c("M1", "M2"))

ATCC_reads <- 
  reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = (ATCC_reads),
    colour = Background
  )) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  ggtitle("Spike-in Viral Reads") +
  ylab("Spike-in Viral Reads") +
  scale_color_manual(values = cols2, labels = c("M1", "M2"))

prop_ATCC <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_ATCC, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
    scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  ggtitle("Spike-in viral reads") +
  ylab("Proportion") +
  scale_color_manual(values = cols2, labels = c("M1", "M2"))

prop_viral <- reads_plot |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(x = Viral.load, y = prop_viral, colour = Background)) +
  geom_point() +
  geom_smooth(aes(group = Background), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
 scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + xlab("Genome copies") +
  # ggtitle("Viral reads") +
  ylab("Proportion of viral reads") +
  scale_color_manual(values = cols2, labels = c("M1", "M2")) + scale_y_continuous(limits=c(0,1.0))

@@

facet_names_bg <- c(
  "dedup_TE" = "Deduplicated",
  "nodedup_TE" = "Non-Deduplicated",
  "p2" = "M1",
  "p8" = "M2"
)

@@

background_counts_reads <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels =
      c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
      )
  ) +
  scale_x_log10(labels = scales::label_log10()) +
  ylab("Log (Viral Reads)")

backgrounds_counts_reads_norm <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts1),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_bw() +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(label = scales::label_log10()) +
  ylab("Log (viral reads/cleaned reads)")

backgrounds_counts_reads_norm2 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(labels = scales::label_log10()) +
  ylab("Log (viral reads/cleaned reads/genome length)")

background_read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray"),
    axis.title.y = element_text(size = 10),
    legend.title = element_blank()
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(label = scales::label_log10()) +
  ylab("Log (mean read depth)")

@@

persite_coverage_both |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  ggplot(aes(x = virus, y = percent_coverage, colour = Background)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_dodge(width = .75)) +
  facet_grid(~as.character(Viral.load), labeller = label_parsed) +
  theme_few() +
  ylab("Genome coverage") +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(values = cols2, labels = c("M1", "M2")) +
  scale_x_discrete(
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_y_continuous(limits = c(0, 1))

@@

coverage_labels3 <-c("100" = "1e+02",
                    "1000" = "1e+03",
                    "100000" = "1e+05",
                    "p2" = "M1",
                    "p8"= "M2")

@@

persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Human_respiratory_syncytial_virus") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id, label = label_parsed) +
  ylab("Coverage") +
  ggtitle("Human RSV (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("M1", "M2"))
```

@@

persite_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  filter(type == "dedup_TE") |>
  filter(virus == "Zika_virus") |>
  rename(Viral.load = `Viral load`) |>
  ggplot(aes(x = site, y = coverage, fill = Background)) +
  geom_col() +
  facet_wrap(Viral.load ~ Sample_id, label = label_parsed) +
  ylab("Coverage") +
  ggtitle("Zika virus (deduplicated)") +
  guides(fill = guide_legend(title = "Background")) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_y_log10() +
  scale_fill_manual(values = cols2, labels = c("M1", "M2"))

@@

facet_names <- c(
  "Msp_p2" = "M1",
  "Msp_p8" = "M2",
  "off_target" = "Background",
  "on_target" = "Spike-in"
)
